Type-Safe Modular Parsing

### 2016-12-12 paper/sections/OpenRecursion.tex
Done text for methodology and library.
Using ruby tool.

\begin{lstlisting}[language=Haskell,keywords={}]
fix f = let x = f x in x
\end{lstlisting}
In Scala, however, there is no library \lstinline{fix} function, but it can be easily implemented since Scala also supports lazy evaluation. See below:
\begin{lstlisting}
def fix[A](f : (=> A) => A) : A = {
    lazy val a : A = f(a)
    a
}
\end{lstlisting}
where function \lstinline{f} has a by-name parameter of type \lstinline{"=>} \lstinline{A"}.
Here we illustrate by the famous Fibonacci example. Traditionally it can be implemented in Scala using pattern-matching:
\begin{lstlisting}
def fib : Int => Int = i => i match {
    case 0 => 0
    case 1 => 1
    case n => fib(n - 1) + fib(n - 2)
}

@@

Another weakness is that the only little extensibility is just fragile when it comes to grammars with multiple different syntax. For instance, in the beginning we only have variables and applications in \lstinline{Expr}, to have types in our language, the \lstinline{Int} type and lambda expressions with annotation are added. See the new grammar below:
\begin{lstlisting}
e ::= x | e ' ' e | \x:t.e
t ::= "Int"
\end{lstlisting}

@@

abstract class Type
case class IntT extends Type
val pInt : (=> Pair) => Parser[Type] =
    p => "Int" ^^ { _ => IntT() }

>>>>

\begin{lstlisting}[language=Haskell,keywords={}]
fix f = let x = f x in x
\end{lstlisting}
In Scala, however, there is no library \lstinline{fix} function, but it can be easily implemented since Scala also supports lazy evaluation. See below:

\lstinputlisting[linerange=27-30]{../Scala/Parser/src/PaperCode/SampleParser.scala}% APPLY:linerange=OPENRECURSION_FIX

where function \lstinline{f} has a by-name parameter of type \lstinline{"=>} \lstinline{A"}.
Here we illustrate by the famous Fibonacci example. Traditionally it can be implemented in Scala using pattern-matching:
\begin{lstlisting}
def fib : Int => Int = i => i match {
    case 0 => 0
    case 1 => 1
    case n => fib(n - 1) + fib(n - 2)
}

@@

Another weakness is that the only little extensibility is just fragile when it comes to grammars with multiple different syntax. For instance, in the beginning we only have variables and applications in \lstinline{Expr}, to have types in our language, the \lstinline{Int} type and lambda expressions with annotation are added. See the grammar below:
\begin{lstlisting}
e ::= x | e ' ' e | \x:t.e
t ::= "Int"
\end{lstlisting}

@@

abstract class Type
case class IntT() extends Type
val pInt : (=> Pair) => Parser[Type] =
    p => "Int" ^^^ IntT()

### 2016-12-12 paper/sections/PackratParsers.tex
Using ruby tool.

\begin{lstlisting}
lexical.reserved += ("str")
lexical.delimiters += ("(", ")")

val p : PackratParser[String] =
    "str" ~> ("(" ~> numericLit <~ ")") ^^ { x => x.toString }
\end{lstlisting}

\noindent

@@

\begin{lstlisting}
def runParser(p: Parser[_]): String => Unit = in => {
    val t = phrase(p)(new lexical.Scanner(in))
    if (t.successful) println(t.get) else scala.sys.error(t.toString)
}
\end{lstlisting}
Now \lstinline{runParser(p)("str(5)")} prints out \lstinline{"5"} as expected.

>>>>

\lstinputlisting[linerange=8-12]{../Scala/Parser/src/PaperCode/SampleParser.scala}% APPLY:linerange=PACKRAT_EXAMPLE
\noindent

@@

\lstinputlisting[linerange=16-19]{../Scala/Parser/src/PaperCode/SampleParser.scala}% APPLY:linerange=PACKRAT_RUNPARSER
Now \lstinline{runParser(p)("str(5)")} prints out \lstinline{"5"} as expected.
